
begin with loading package

```{r}
library(readr)
library(ggplot2)
library(scales)
library(dplyr)
```


Code for reading in the dataset and/or processing the data. 
BE CAREFUL, THIS IS WORKING WITH FRENCH DATE


```{r}
setwd("C:/Users/giffonev/Dropbox/TPR/reproducible-research-1")

activity <- read_csv("activity.csv", col_types = cols(steps = col_integer()))
activity$date <- as.Date(activity$date,format="%Y/%m/%d")
g <- ggplot(data=activity,aes(x=activity$date, y=activity$steps))
h <- ggplot(data=activity,aes(x=activity$interval, y=activity$steps))
activity$week <- 

     

activity$week <- sapply(activity$date,weekdays)
 for (i in 1:length(activity$steps)) {
    if (activity$week[i] == "samedi") {
         activity$week[i] <- "weekend"
    } else if (activity$week[i] == "dimanche") {
         activity$week[i] <- "weekend"
    } else {
         activity$week[i] <- "weekday"
    }
 }
activity$week <- as.factor(activity$week)
```

Histogram of the total number of steps taken each day

```{r}

g + geom_bar(stat = "identity") + labs(title = "Histogram of the total number of steps taken each day", x = "day", y = "total step per day") 

```



Mean and median number of steps taken each day
```{r}

g + stat_summary(fun.y=mean, geom="point", shape=1, size = 1.5, col = "red") + labs(title = "mean number of steps taken each day", x = "day", y = "mean step per day") + scale_x_date(labels = date_format("%m/%d"), breaks = "week") 

g + stat_summary(fun.y=median, geom="point", shape=1, size = 1.5, col = "red") + labs(title = "median number of steps taken each day", x = "day", y = "mean step per day") + scale_x_date(labels = date_format("%m/%d"), breaks = "week") 


```

Time series plot of the average number of steps taken
```{r}
h + stat_summary(fun.y=mean, geom="point", shape=1, size = 1.5, col = "red") + labs(title = "Time series plot of the average number of steps taken", x = "time ", y = "mean step per time series") 
```

The 5-minute interval that, on average, contains the maximum number of steps
```{r}

test <- tapply(activity$steps,activity$interval,mean, na.rm=TRUE)
max(test)
```

Code to describe and show a strategy for imputing missing data
```{r}
#number of NA : 
sum(is.na(activity$steps))

#replacing NA with the mean : 
activity$steps[is.na(activity$steps)] <- mean(activity$steps, na.rm  = TRUE)
sum(is.na(activity$steps))
```

Histogram of the total number of steps taken each day after missing values are imputed
```{r}
j <- ggplot(data=activity,aes(x=activity$date, y=activity$steps))
j + geom_bar(stat = "identity") + labs(title = "Histogram of the total number of steps taken each day after missing values are imputed", x = "day", y = "total step per day") 
 
```

Panel plot comparing the average number of steps taken per 5-minute interval across weekdays and weekends

```{r}
k <- ggplot(data=activity,aes( x = activity$date, y=activity$steps, color = activity$week)) 
k + stat_summary(fun.y=mean, geom="line", size = 1) 
```

All of the R code needed to reproduce the results (numbers, plots, etc.) in the report



setwd("C:/Users/giffonev/Dropbox/TPR/reproducible-research-1")

activity <- read_csv("activity.csv", col_types = cols(steps = col_integer()))
activity$date <- as.Date(activity$date,format="%Y/%m/%d")
g <- ggplot(data=activity,aes(x=activity$date, y=activity$steps))
h <- ggplot(data=activity,aes(x=activity$interval, y=activity$steps))
activity$week <- 

     

activity$week <- sapply(activity$date,weekdays)
 for (i in 1:length(activity$steps)) {
    if (activity$week[i] == "samedi") {
         activity$week[i] <- "weekend"
    } else if (activity$week[i] == "dimanche") {
         activity$week[i] <- "weekend"
    } else {
         activity$week[i] <- "weekday"
    }
 }
activity$week <- as.factor(activity$week)


Histogram of the total number of steps taken each day



g + geom_bar(stat = "identity") + labs(title = "Histogram of the total number of steps taken each day", x = "day", y = "total step per day") 





Mean and median number of steps taken each day


g + stat_summary(fun.y=mean, geom="point", shape=1, size = 1.5, col = "red") + labs(title = "mean number of steps taken each day", x = "day", y = "mean step per day") + scale_x_date(labels = date_format("%m/%d"), breaks = "week") 

g + stat_summary(fun.y=median, geom="point", shape=1, size = 1.5, col = "red") + labs(title = "median number of steps taken each day", x = "day", y = "mean step per day") + scale_x_date(labels = date_format("%m/%d"), breaks = "week") 




Time series plot of the average number of steps taken

h + stat_summary(fun.y=mean, geom="point", shape=1, size = 1.5, col = "red") + labs(title = "Time series plot of the average number of steps taken", x = "time ", y = "mean step per time series") 


The 5-minute interval that, on average, contains the maximum number of steps


test <- tapply(activity$steps,activity$interval,mean, na.rm=TRUE)
max(test)


Code to describe and show a strategy for imputing missing data

#number of NA : 
sum(is.na(activity$steps))

#replacing NA with the mean : 
activity$steps[is.na(activity$steps)] <- mean(activity$steps, na.rm  = TRUE)
sum(is.na(activity$steps))


Histogram of the total number of steps taken each day after missing values are imputed

j <- ggplot(data=activity,aes(x=activity$date, y=activity$steps))
j + geom_bar(stat = "identity") + labs(title = "Histogram of the total number of steps taken each day after missing values are imputed", x = "day", y = "total step per day") 
 


Panel plot comparing the average number of steps taken per 5-minute interval across weekdays and weekends

k <- ggplot(data=activity,aes( x = activity$date, y=activity$steps, color = activity$week)) 
k + stat_summary(fun.y=mean, geom="line", size = 1) 





